%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{fancyvrb}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage[colorinlistoftodos]{todonotes}

%----------------------------------------------------------------------------------------
%   HEADING
%----------------------------------------------------------------------------------------

\newcommand{\BigO}[1]{\ensuremath{\operatorname{O}\left(#1\right)}}

\title{\textsc{Software Engineering}\\Feedback}
\author{Lawrence Jones \{lmj112\}}

\date{}
\begin{document}
\maketitle

%----------------------------------------------------------------------------------------
%   BODY
%----------------------------------------------------------------------------------------

Firstly, I really enjoyed the course and thought it offered a valuable
experience with such a different format to the rest of my degree. Few modules
have allowed for such interaction with my peers about content that is directly
relevant to the work I intend to pursue beyond university.

The weekly essays were a great way for me to get back into practise with
critical writing. Essay based handins are so few in an Imperial Computing
degree, and feedback is typically less focussed on writing style, so forcing
myself to write every week enabled me to recall some of the skills that have
become rusty since I left sixth-form. This has direct applicability to my
professional career, as well as serving as a wake-up before tackling my final
project report.

A criticism of the format would be that the divide between the practical side of
the weekly handins and the writing was ambiguous. We were never sure if the
practical would contribute to our grade, or if we were to use it as inspiration
for the writing. Some extra clarity about how to split the work would be
appreciated.

I would suggest that quotes not be included in the word count for the final
article, as we spent many hours cutting 500 words that we really felt added to
the piece, but I'm sure you'll suggest we should learn to be more concise! \\

Thank you for a really enjoyable course!

\end{document}
